\documentclass{article}
\usepackage{../fasy-hw}

%% UPDATE these variables:
\renewcommand{\hwnum}{0}
\title{Discrete Structures, Homework \hwnum}
\author{\todo{Brendan- Gibson}}
\collab{\todo{N/A}}
\date{due: 30 August 2021}

\begin{document}

\maketitle

This homework assignment should be
submitted as a single PDF file both to D2L and to Gradescope.

General homework expectations:
\begin{itemize}
    \item Homework should be typeset using LaTex.
    \item Answers should be in complete sentences and proofread.
    \item You will not plagiarize, nor will you share your written solutions
        with classmates.
    \item List collaborators at the start of each question using the
        \texttt{collab} command.
    \item Put your answers where the \texttt{todo} command currently is (and
        remove the \texttt{todo}, but not the word \texttt{Answer}).
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\collab{N/A}
\nextprob{Getting to Know You}

Answer the following questions:
\begin{enumerate}
    \item What is your elevator pitch?  Describe yourself in 1-2
                sentences.

        \paragraph{Answer} \todo{I am a work-in-progress reinessence man, faithful to the state of Montana. Math is my profession, but writing is my passion.}

     \item What was your favorite CS class so far, and why?

         \paragraph{Answer} \todo{My favorite CS class was ---. I saw practical and industrial applications of programming and computational power.}

     \item What was your least favorite CS class so far, and why?

         \paragraph{Answer} \todo{My least favorite course was ---. The professor was good, but the theory was dense and intitially confusing.}

     \item Why are you interested in taking this course?

         \paragraph{Answer} \todo{I am interested in this course because I think I will learn more alogrithms and CS concepts that will assits my mathematical education. This class also seemed like a good choice for my CS minor.}

     \item What is your biggest academic or research goal for this semester (can
         be related to this course or not)?

         \paragraph{Answer} \todo{My biggest academic goal is to line up a profession whilst maintaining good academic peformance.}

     \item What do you want to do after you graduate?

         \paragraph{Answer} \todo{I want to find work--ideally in Kalispell.}

     \item What was the most challenging aspect of your coursework last semester?

         \paragraph{Answer} \todo{The most challenging aspect was my attidute. I seldom asked for help and had a sour mood when doing my coursework.}

    \item Is your photo in D2L a recognizable photo of yourself?  (Note: the
        answer should be ``Yes'').

         \paragraph{Answer} \todo{Yes.}

\end{enumerate}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\collab{N/A}
\nextprob{Discussion Board}

Make a post in the class discussion board. No answer needs to be written here.
But, for bonus points, include a screenshot of your post.


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\collab{\todo{}}
\nextprob{Plagiarism}

\begin{enumerate}

    \item In this class, please properly cite all resources that you use. Please
        write your own definition of plagiarism here.  Remember to cite all
        sources!

        \paragraph{Answer}
        \todo{Plagarism: to use another person's work, but under the guise that the work is your own.}

    \item If you have observed plagiarism or cheating in a classroom (either as
        an instructor or as a student), explain the situation and how it made
        you feel.  If you have not experienced plagiarism or cheating or if you
        would prefer not to reflect on a personal experience, find a news
        article about plagiarism or cheating and explain how you would feel if
        you were one of the people involved.

        \paragraph{Answer}
        \todo{https://jesuitroundup.org/viewpoint/viewpoint-student-life/cheating-why-do-students-do-it/ //
        I tend to think in black-and-white morality. To witness cheating would disgust me, not only because I think it's wrong, but also because its such blatant self-sabotage.}
\end{enumerate}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\collab{\todo{}}
\nextprob{Edges in Trees}

Prove or disprove the following statement: Every tree with one or more
nodes/vertices has exactly $n-1$ edges, where $n$ is the number of vertices in
the tree.

\paragraph{Answer}

\todo{}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\collab{\todo{}}
\nextprob{Big-O}
Use the definition of big-O notation to prove that $f(x)=n^2 + 3n -2$ is
$O(n^2)$.

\paragraph{Answer}

\todo{}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\collab{\todo{}}
\nextprob{If/Then Statements}
Consider the following statement: If $a$ and $b$ are both even numbers, then $ab$ is
an even number.
\begin{enumerate}
    \item What is the definition of an odd number?

        \paragraph{Answer}
        \todo{}

    \item What is the definition of an even number?

        \paragraph{Answer}
        \todo{}

    \item What is the contrapositive of this statement?

        \paragraph{Answer}
        \todo{}

    \item What is the converse of this statement?

        \paragraph{Answer}
        \todo{}

    \item Prove this statement.

        \paragraph{Answer}
        \todo{}

\end{enumerate}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\collab{\todo{}}
\nextprob{Sorting}
Consider your favorite sorting algorithm.
\begin{enumerate}
    \item \emph{What} is the problem that this algorithm solves?

        \paragraph{Answer}
        \todo{}

    \item \emph{How} does it work? (Hint: give pseudocode!)

        \paragraph{Answer}
        \todo{}

    \item \emph{How fast} does it work?  Give the asymptotic running time.
        Note: typically, you will give this as the worst-case running time.
        However, if you chose quicksort or another randomized algorithm, please
        give both the worst-case running time and the expected running time.  No
        justification of the running time is needed.

        \paragraph{Answer}
        \todo{}

    \item \emph{Why} does this work? Typically, this will be given as a loop
        invariant proof.  For this HW, explain why it works informally, in your
        own words.

        \paragraph{Answer}
        \todo{}

\end{enumerate}

Note: in all future HWs, if you are asked to come up with an algorithm, you are
expected to give an algorithm that beats the brute force (and, if possible, of
optimal time complexity). With your algorithm, please provide the following:
\begin{itemize}
    \item \emph{What}: A prose explanation of the problem and the algorithm,
        including a description of the input/output.
    \item \emph{How}: Psuedocode, referenced from within the prose explanation.
    \item \emph{How Fast}: Runtime, along with justification.  (Or, in the
        extreme, a proof of termination).
    \item \emph{Why}: Statement of the loop invariant for each loop.
\end{itemize}

\end{document}
